### 2018-05-05 papers/synth/example.tex
printing

\input{fig-mukund-vts}

In figure~\ref{fig:mukund-vts}, we present the VTS for mammalian cells
obtained by studying the literature.
%
The

% and hollow arrows represent maturation edges.

We have used our tool to synthesize possible fixes to complete the
graph. Based on the variation we were able to synthesis the this graph
within 600s. We have created a rank of minimum edits to complete the
graph. Our experiments suggest that the synthesis problems are
solvable by modern solvers and the synthesis technology may be useful
for biological research.

>>>>

% \input{fig-mukund-vts}

### 2018-05-05 papers/synth/intro.tex

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on two found-in-nature
VTSs~\cite{burri2004complete}.
%
We have also applied our tool on various synthetic examples to
demonstrate that our tool scale upto the graph size size nodes, which
is the size of typical VTSs in a eukaryotic cell.

The following are the contributions of this work:
\begin{itemize}
\item We have identified an interesting application of
  the synthesis technology.
\item We have developed encoding of the synthesis problem in QBF.
\item A user friendly and scalable tool based on a well known SMT solver Z3
\end{itemize}

The rest of the paper is organized as follows.
%
In section~\ref{sec:example}, we present a motivating example.
%
In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
constraints on VTSs.
%
In section~\ref{sec:encoding}, we present the synthesis problems and their
encoding into QBF satisfiability.
%
In section~\ref{sec:experiments}, we present our implementation and experimental results.
%
We discuss related work in~\ref{sec:related} and conclude in section~\ref{sec:conclusion}.

>>>>

We have implemented the encoding in a flexible tool,
which can handle a wide range of synthesis query.
%
We have applied our tool on two found-in-nature
VTSs~\cite{burri2004complete}.
%
In figure~\ref{fig:mukund-vts}, we present one of the two for
mammalian cells obtained by studying the
literature.\footnote{Please read appendix~\ref{sec:ex-vts} for more biological details.}
%
The VTS has six nodes and 20+ molecules.
%
We can easily check that stability condition is not satisfied for
many molecules for example ???.
%
It is clear that there are several unknowns about the VTS.
%
%
% Our tool 
% % and hollow arrows represent maturation edges. 
% We have used our tool to synthesize possible fixes to complete the
% graph.
% %
% Based on the variation we were able to synthesis the this graph
% within ??s.
%
Our synthesis tool reports that minimum ?? edges needs to be added to make
the VTS stable.
%
Our experiments suggest that the synthesis problems are
solvable by modern solvers and the synthesis technology may be useful
for biological research.
%
We have also applied our tool on various synthetic examples to
demonstrate that our tool scale upto the graph size size nodes, which
is the size of typical VTSs in a eukaryotic cell.

The following are the contributions of this work:
\begin{itemize}
\item We have identified an interesting application of
  the synthesis technology.
\item We have developed encoding of the synthesis problem in QBF.
\item A user friendly and scalable tool based on QBF solvers
\end{itemize}

The rest of the paper is organized as follows.
%
% In section~\ref{sec:example}, we present a motivating example.
% %
In section~\ref{sec:prelim}, we present the graph model of VTSs and encoding of several
constraints on VTSs.
%
In section~\ref{sec:encoding}, we present the synthesis problems and their
encoding into QBF satisfiability.
%
In section~\ref{sec:experiments}, we present our implementation and experimental results.
%
We discuss related work in~\ref{sec:related} and conclude in section~\ref{sec:conclusion}.

\input{fig-mukund-vts}
